Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-05 edubots_surveys.Rnw
Pimmer et al. update in the literature review section

Initially, a single survey was developed for this purpose and responses from 300 higher education teachers were collected and analysed. 
The responses' analysis entailed the creation of a second survey to which 200 teachers' responses were collected. The questions of the second 
survey focussed on discussing teachers' needs, opinions and preferences of the development of future technology-enhanced tools 
and its' potential impact on educational institutions’ policies. Therefore, this paper investigated the following research questions:

\begin{itemize}
\item RQ1 - Are teachers already using messaging apps in their classes? 
\item RQ2 - Which chatbots' features would teachers find useful in their classes? 
\item RQ3 - Which kind of interaction do teachers prefer with their students?
\item RQ4 - What kind of interaction media features do teachers value the most?
\end{itemize}

>>>>

Initially, a single survey was developed for this purpose. Responses from 300 teachers were collected and analysed. An initial analysis of these responses led to the creation of a second survey, which collected responses from 200 different higher education teachers. The questions on this survey focus on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions:

\begin{itemize}
\item RQ1 - Are teachers already using messaging apps in their classes? 
\item RQ2 - Which kind of chatbots would teachers find useful in their classes? 
\item RQ3 - Which kind of interaction do teachers prefer with their students?
\item RQ4 - What kind of interaction media features do teachers value the most?
\end{itemize}
